---
title: "practice_ggvis"
author: "Sky Liu"
date: "12/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(
  "ggvis",
  "dplyr",
  "shiny"
)
```

## Overview

This file is a quick learning of ggvis package.
ggvis is a package for interactive data visualization in R. It is similar to ggplot2. The biggest character of this package is that it combines the best of R and web so it could be used at a local Rstudio or on a webpage. 

The tutorial is found from Rblogger. The link to the tutorial
is:
https://ggvis.rstudio.com
https://ggvis.rstudio.com/cookbook.html
https://ggvis.rstudio.com/interactivity.html
https://github.com/rstudio/ggvis/tree/master/demo/apps/basic



##Application

We use the built-in data **ToothGrowth**

```{r}
data("USArrests")
data<-as.data.frame(USArrests)
head(USArrests)
```
###Scatterplot with Regression Line
```{r}
data %>% 
  ggvis(~UrbanPop, ~Murder) %>%
  layer_points() %>%
  layer_model_predictions(model = "lm", se = TRUE)
```
###Histogram
```{r}

data %>% ggvis(~Murder) %>% layer_histograms(width=0.5, boundary=0)
```
###Adding Interaction

```{r}

data %>% 
  ggvis(~Murder) %>% 
  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
                   center = input_slider(0, 2, step = 0.05, label = "center"))
```